Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-06-07 writeups/psycMethods/psycMethods.tex
foo

Model accuracy was tested on the popular-hashtags dataset for Twitter and a random sample of posts across the entire StackOverflow dataset.
For each of the four Twitter popular-hashtags datasets, model retrievals were done across 15 runs and 500 posts within each run.
For the StackOverflow randomly-sampled dataset, 5 runs of 100 posts were used,
since the results for StackOverflow were more stable and retrievals took more wall-clock time for this dataset due to the size of the co-occurrence matrix.
All runs contained different posts, and all posts used for runs were not used to generate the co-occurrence matrix for the two retrieval models.

>>>>

Model accuracy was tested on the popular-hashtags dataset for Twitter and a random sample of posts across the entire StackOverflow dataset.
For each of the four Twitter popular-hashtags datasets, model retrievals were done across 15 runs and 500 posts within each run.
For the StackOverflow randomly-sampled dataset, 5 runs of 500 posts were used,
since the results for StackOverflow were more stable and retrievals took more wall-clock time for this dataset due to the size of the co-occurrence matrix.
All runs contained different posts, and all posts used for runs were not used to generate the co-occurrence matrix for the two retrieval models.
